Exact Asymptotics for Causal Mediation Analysis

### 2024-05-08 notes/William Analysis.Rmd
Fix SEs for bin-bib-fix

```{r, boilerplate, include=FALSE, cached=TRUE}
# Note: This code chunk is not run here, but it is called and run at the start of every subsequent section. Any changes made here will be duplicated throughout the rest of the document.

@@

```{r, cache=TRUE, dependson=c("boilerplate")}

@@

```{r, cache=TRUE, dependson=c("boilerplate")}

@@

```{r, cache=TRUE, dependson=c("boilerplate")}

@@

    ## Linear predictor for M
    eta_hat = a_0_hat + a_x_hat*x_pred + W_pred%*%A_2_hat
    zeta_hat = b_0_hat + b_x_hat * x_pred + W_pred %*% B_3_hat

    # Mediation effect
    ## See Helpers.R for the function get_odds_ratio
    med_hat = get_odds_ratio(eta_hat, a_x, zeta_hat, b_x, b_m)
    some_med_hats[[i]] = med_hat

>>>>

```{r, boilerplate}
# , cached=TRUE}
# Note: This code chunk is not run here, but it is called and run at the start of every subsequent section. Any changes made here will be duplicated throughout the rest of the document.

@@

```{r MC-cont-cont-fix, include=FALSE, cache=TRUE}
# , dependson=c("boilerplate")}

@@

```{r MC-cont-bin-fix, include=FALSE, cache=TRUE}
# , dependson=c("boilerplate")}

@@

```{r MC-bin-bin-fix, include=FALSE, cache=TRUE}
# , dependson=c("boilerplate")}

@@

    ## Linear predictor for M
    eta_hat = a_0_hat + a_x_hat*x_pred + W_pred%*%A_2_hat
    zeta_hat = b_0_hat + b_x_hat*x_pred + W_pred %*% B_3_hat

    # Mediation effect
    ## See Helpers.R for the function get_odds_ratio
    med_hat = get_odds_ratio(eta_hat, a_x_hat, zeta_hat, b_x_hat, b_m_hat)
    some_med_hats[[i]] = med_hat
